Measurement of nuclear excitation functions for proton induced reactions (E$_{\text{p}}$ = 40 -- 90 MeV) on natural Nb and Cu

### 2017-12-08 nb_px_paper/nb_px_paper.tex
Finished sections 4 & 5

In summation, we present here a set of 38 measurements of cross sections for the \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40.34 - 89.74 MeV, as well as 5 independent measurements of isomer branching ratios.
Nearly all cross sections have been reported with smaller uncertainties than previous measurements, and we report the first measurements of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, as well as the first measurement of the independent cross sections for    \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40 - 90 MeV region.

@@

 Michael Gallegos and Don Dry in the C-NR Countroom, David Reass and Mike Connors at IPF, and the LANSCE Accelerator Operations staff

>>>>

In summation, we present here a set of 38 measurements of cross sections for the \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions between 40.34 - 89.74 MeV, as well as 5 independent measurements of isomer branching ratios.
Nearly all cross sections have been reported with smaller uncertainties than previous measurements, and we report the first measurements of the  \ce{^{nat}Nb}(p,x)\ce{^{82m}Rb} reaction, as well as the first measurement of the independent cross sections for    \ce{^{nat}Cu}(p,x)\ce{^{52\text{m}}Mn}, \ce{^{nat}Cu}(p,x)\ce{^{52\text{g}}Mn}, and \ce{^{nat}Nb}(p,x)\ce{^{85\text{g}}Y} in the 40 - 90 MeV region.
We also use these measurements to illustrate the impact of pre-equilibrium particle emission in the reaction dynamics for 40 - 90 MeV \ce{^{nat}Nb}(p,x) and  \ce{^{nat}Cu}(p,x) reactions.
Finally, this work provides another example of the usefulness of the recently-described variance minimization techniques for reducing energy uncertainties in stacked target charged particle irradiation experiments.

@@

 The authors would like to particularly acknowledge the assistance and support of  Michael Gallegos and Don Dry in the LANL C-NR Countroom, David Reass and Mike Connors at LANSCE-IPF, and the LANSCE Accelerator Operations staff.
